---
title: "DATA607"
author: "[Kleber Perez - `r format(Sys.Date(), '%B %d, %Y')`](https://www.linkedin.com/in/kleberperez/)" 
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<div class="jumbotron jumbotron-fluid">
  <div class="container">
  <div class="btn btn-warning btn-block">
  <h1 class="btn btn-warning btn-block">Week 3 Assignment</h1>
  <br />
  <p class="lead">Please deliver links to an R Markdown file (in GitHub and rpubs.com) <br />
    Problem 9 is extra credit.
  </p>
  <hr class="my-4">
  <a class="btn btn-dark btn-lg" href="http://r-datacollection.com/" role="button">R-Datacollection</a>
  <br />

  </div>
</div>

<div class="jumbotron jumbotron-fluid">
  <div class="container">
  <p class="lead">&#51; Copy the introductory example. The vector <span class="badge badge-info">name</span> stores the extracted <span class="badge badge-info">names</span>

  </p>
  <hr class="my-4">

```{r}
library(stringr)
library(knitr)

raw.data <- "555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"

name <- unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))
phone <- unlist(str_extract_all(raw.data, "\\(?(\\d{3})?\\)?(-| )?\\d{3}(-| )?\\d{4}"))
name
kable(data.frame(name,phone))

```
  
  </div>
</div>


<div class="jumbotron jumbotron-fluid">
  <div class="container">
  <p class="lead">&#51; (a). Use the tools of this chapter to rearrange the vector so that all elements conform to the standard firstname last_name.
  </p>
  <hr class="my-4">

```{r}
name2 <- sub(" [A-z]{1}\\. "," ",name)
name3 <- sub("(\\w+),\\s(\\w+)","\\2 \\1", name2)
first_and_lastname <- sub("[A-z]{2,3}\\. ","",name3)
kable(data.frame(first_and_lastname))
```
  
  </div>
</div>


<div class="jumbotron jumbotron-fluid">
  <div class="container">
  <p class="lead">&#51; (b). Construct a logical vector indicating whether a character has a title.
  </p>
  <hr class="my-4">

```{r}
title <- str_detect(name3,"[A-z]{2,3}\\. ")
df <- data.frame(name3, title)
kable(data.frame(df))
```
  
  </div>
</div>

`
<div class="jumbotron jumbotron-fluid">
  <div class="container">
  <p class="lead">&#51; (c). Construct a logical vector indicating whether a character has a second name.
  </p>
  <hr class="my-4">

```{r}
secondname <- str_detect(name," [A-z]{1}\\. ")
df <- data.frame(name, secondname)
df
```
  
  </div>
</div>


`
<div class="jumbotron jumbotron-fluid">
  <div class="container">
  <p class="lead">&#52; Describe the tyoes of strings that conform to the following regular expressions and
  construct an exmaple that is matched by the regular expression.
  </p>
  <p class="lead">&#52; (a). [0-9] +\\$         #One or more numbers followed by $ symbol.
  </p>

```{r}
library(stringr)
example <- c ("12$", "45$")
str_detect(example, "[0-9]+\\$")
```
  
  </div>
</div>


`
<div class="jumbotron jumbotron-fluid">
  <div class="container">
  <p class="lead">&#52;(b) \\b[a-z]{1,4}\\b   #A word contains 1 to 4 letters.
  </p>

```{r}
example2 <- c("ok", "four")
str_detect(example2, "\\b[a-z]{1,4}\\b" )
```
  
  </div>
</div>

`
<div class="jumbotron jumbotron-fluid">
  <div class="container">
  <p class="lead">&#52; (c) .*?\\.txt$          #string ends with .txt
  </p>

```{r}
pattern3=".*?\\.txt$"
example3=c(".txt","123.txt","abc.txt","a$b#1.txt")
str_detect(example3,pattern3)
```
  
  </div>
</div>

`
<div class="jumbotron jumbotron-fluid">
  <div class="container">
  <p class="lead">&#52; (d). \\d{2}/\d{2}/\\d{4}  #numbers have format in nn/nn/nnnn
  </p>

```{r}
example4 <- c("01/09/1991", "08/14/1965")
str_detect(example4, "\\d{2}/\\d{2}/\\d{4}")
```
  
  </div>
</div>

`
<div class="jumbotron jumbotron-fluid">
  <div class="container">
  <p class="lead">&#52; (e) <(.+?)>.+?</\\1>    #characters inside <> followed by another charater in the <> with / in it.
  </p>

```{r}
example5 <- c("<tag>Text</tag>")
str_detect(example5, "<(.+?)>.+?</\\1>")
```
  
  </div>
</div>

`
<div class="jumbotron jumbotron-fluid">
  <div class="container">
  <div class="btn btn-warning btn-block">
  <p class="lead">Problem 9
  </p>
  <p class="lead">The following code hides a secret message.
  </p>

```{r}
secret_message <- paste("clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0Tanwo
Uwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigO
d6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5
fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr") 
message <- unlist(str_extract_all(secret_message, "[[:upper:].]{1,}"))
message <- str_replace_all(paste(message, collapse = ''), "[.]", " ")
message

the_end<- paste("3nc4gxo5nhk!gr.Tanwor1w1H4dr3cocfE9.2bk4fE89n6N5nhDk!.") #!gr .--Added after this..
the_end <- unlist(str_extract_all(the_end, "[[:upper:].]{1,}"))
the_end <- str_replace_all(paste(the_end, collapse = ''), "[.]", " ")
the_end
```
  
  </div>
  </div>
</div>


<br />
<br />

> *Please email to: * <a href="mailto:kleber.perez@live.com">kleber.perez@live.com</a> *for any suggestion.*

<footer class="border-top text-muted fixed-bottom">

        Data607 Week 3 Assignment - MSDS 2019 Program.

</footer>

\textbf{Text ignored: END of other links}

<br />
<br />
